Verifying Demonstrations

### 2018-05-25 paper/DB-anon-cred.tex
Corrects DBS: only one random value

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to two random values and the verifier sends two challenges.
Afterwards, the verifier presents to the prover which commitment and challenge to use during the \ac{DB} phase.

\begin{figure*}
  \centering
  \begin{tabular}{lcl}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

    \(\rho_0\rgets \ZZ_q, \rho_1\rgets \ZZ_q\)
    &
    &
    \\

    \(R_0\gets g^{\rho_0}, R_1\gets g^{\rho_1}\)
    & \(\ProtoSendRight{R_0, R_1}\)
    &
    \\

@@

    \(s_0\gets \rho_0 + c_0\alpha\)
    &
    &
    \\

    \(s_1\gets \rho_1 + c_1\alpha\)
    &
    &
    \\

    % null
    &
    & \(b\rgets \bin\)
    \\

    % null
    &
    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\),
    \\

    % null
    &
    & with \(\ceil{\log_2 q}\) bits set to \(b\)
    \\

@@

    % null
    &
    & \(r = r_1|\dotsb|r_{\ceil{\log_2 q}}\)
    \\

    % null
    &
    & \(R_b \stackrel{?}{=} g^r A^{c_b}\)
    \\

>>>>

We present the protocol in \cref{SchnorrFigure}.
The difference from the original Schnorr protocol is that the prover commits to 
one random value but the verifier sends two challenges.
The verifier presents to the prover which commitment and challenge to use 
during the \ac{DB} phase.

\begin{figure*}
  \centering
  \begin{tabular}{p{5cm}cp{5cm}}
    \(\DBSprove[g, q, \alpha, A = g^\alpha]\):
    & &
    \(\DBSverify[g, q, A]\):
    \\
    \midrule

@@

    \(\rho\rgets \ZZ_q, R\gets g^{\rho}\)
    & \(\ProtoSendRight{R}\)
    &
    \\

@@

    \(s_0\gets \rho + c_0\alpha \pmod q\)
    &
    & \(b\rgets \bin\)
    \\

    \(s_1\gets \rho + c_1\alpha \pmod q\)
    &
    & Prepare \(B\in \bin^{\ceil{\log_2 q}+l}\), with \(\ceil{\log_2 q}\) bits 
    set to \(b\).
    \\

@@

    % null
    &
    & Construct \(r = s_b\) as the concatenation of \(r_i\)'s for which \(b_i = 
      b\).
    \\

    % null
    &
    & \(R \stackrel{?}{=} g^r A^{c_b}\)
    \\
